Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-12 concurrency/CONCUR 2023/paper.tex
WIP verified lock-coupling

$$\forall \texttt{t}.\ \left\langle \nodeboxrep \texttt{(pn)} 
%\ast \lockinv \texttt{(pn->p->lock,R'}) 
\ast \texttt{R(pn->p)} \ | \ \treerep\ \texttt{t} \right\rangle $$
$$\texttt{traverse(pn, k)}$$
$$\left\langle \texttt{res}, \texttt{n'}. \ \nodeboxrep \texttt{(pn)}
%ast \lockinv \texttt{(pn->n'->lock,R')} 
\ast \texttt{R(pn->n')} \ast (\texttt{k} \in \texttt{range}) \ast (\texttt{res} \leftrightarrow (\texttt{pn->n'->t} = \texttt{NULL}))
\   |\ \treerep\ \texttt{t} \right\rangle$$

@@

The specification says ....

The key to the verification of \texttt{traverse} function is the loop invariant for the top-level loop. We define the loop invariant for \texttt{traverse} function of lock-coupling style as follows:

$$
\texttt{traverse\_inv} 
$$

>>>>

$$\forall \texttt{t}.\ \left\langle \nodeboxrep \texttt{(pn)} 
%\ast \lockinv \texttt{(pn->p->lock,R'}) 
\ast \texttt{R(pn->p)} \ | \ \treerep\ \texttt{t} \right\rangle $$
$$\texttt{traverse(pn, k)}$$
$$\left\langle \texttt{res} \ \texttt{n'}. \ (\texttt{res} \leftrightarrow (\texttt{pn->n'->t} = \texttt{NULL})) \ast \nodeboxrep \texttt{(pn)}
%ast \lockinv \texttt{(pn->n'->lock,R')} 
\ast \texttt{R(pn->n')} \ast (\texttt{k} \in \texttt{range})
\   |\ \treerep\ \texttt{t} \right\rangle$$

@@

The specification states that if the node \texttt{p} is within the footprint of the search structure, then the \texttt{traverse} function operates on the entire search structure and returns a subsequent node \texttt{n'}, where \texttt{k} falls within the range of node \texttt{n'}.

The key to the verification of \texttt{traverse} function is the loop invariant for the top-level loop. We define the loop invariant for \texttt{traverse} function of lock-coupling style as follows: 
\begin{align*} &\mathsf{traverse\_inv}() \triangleq\ \exists\ (x\in \mathit{range})\land \texttt{R(pn->p)} \ast  \nodeboxrep(b,\mathit{g\_root})\ \ast \cdots 
\end{align*}
